
\documentclass[letterpaper,11pt,oneside]{article}
% \documentclass[a4paper,11pt,oneside]{article}
\usepackage{ifthen}
\usepackage{longtable}
\usepackage{setspace}
\usepackage[left=.4in,right=.4in,top=0.7in,bottom=0.5in,nohead,nofoot]{geometry}
\usepackage{marvosym}
\usepackage{times}
\usepackage[usenames,dvipsnames]{color}
\usepackage{graphicx}

\usepackage{enumitem}
\setlist{noitemsep, topsep=0pt, parsep=0pt, partopsep=0pt, leftmargin=0cm}

\usepackage[bookmarks,
pdftitle={Resume},
pdfauthor={Sharmila Duppala},
pdfsubject={},
pdfcreator={},
pdfproducer={},
pdfkeywords={},
pdfpagemode={},
pdfstartview=FitH,
colorlinks=true,
linkcolor=black,   %Color for normal internal links.
anchorcolor=black, %Color for anchor text.
citecolor=green,   %Color for bibliographical citations in text.
filecolor=magenta, %Color for URLs which open local files.
menucolor=red,     %Color for Acrobat menu items.
urlcolor=black]{hyperref}

\newcommand{\longmonth}[1]{%
    \ifthenelse{\equal{#1}{1}}{January}{}%
\ifthenelse{\equal{#1}{2}}{February}{}%
\ifthenelse{\equal{#1}{3}}{March}{}%
\ifthenelse{\equal{#1}{4}}{April}{}%
\ifthenelse{\equal{#1}{5}}{May}{}%
\ifthenelse{\equal{#1}{6}}{June}{}%
\ifthenelse{\equal{#1}{7}}{July}{}%
\ifthenelse{\equal{#1}{8}}{August}{}%
\ifthenelse{\equal{#1}{9}}{September}{}%
\ifthenelse{\equal{#1}{01}}{January}{}%
\ifthenelse{\equal{#1}{02}}{February}{}%
\ifthenelse{\equal{#1}{03}}{March}{}%
\ifthenelse{\equal{#1}{04}}{April}{}%
\ifthenelse{\equal{#1}{05}}{May}{}%
\ifthenelse{\equal{#1}{06}}{June}{}%
\ifthenelse{\equal{#1}{07}}{July}{}%
\ifthenelse{\equal{#1}{08}}{August}{}%
\ifthenelse{\equal{#1}{09}}{September}{}%
\ifthenelse{\equal{#1}{10}}{October}{}%
\ifthenelse{\equal{#1}{11}}{November}{}%
\ifthenelse{\equal{#1}{12}}{December}{}}

\newcommand{\shortmonth}[1]{%
    \ifthenelse{\equal{#1}{1}}{Jan}{}%
\ifthenelse{\equal{#1}{2}}{Feb}{}%
\ifthenelse{\equal{#1}{3}}{Mar}{}%
\ifthenelse{\equal{#1}{4}}{Apr}{}%
\ifthenelse{\equal{#1}{5}}{May}{}%
\ifthenelse{\equal{#1}{6}}{Jun}{}%
\ifthenelse{\equal{#1}{7}}{Jul}{}%
\ifthenelse{\equal{#1}{8}}{Aug}{}%
\ifthenelse{\equal{#1}{9}}{Sep}{}%
\ifthenelse{\equal{#1}{01}}{Jan}{}%
\ifthenelse{\equal{#1}{02}}{Feb}{}%
\ifthenelse{\equal{#1}{03}}{Mar}{}%
\ifthenelse{\equal{#1}{04}}{Apr}{}%
\ifthenelse{\equal{#1}{05}}{May}{}%
\ifthenelse{\equal{#1}{06}}{Jun}{}%
\ifthenelse{\equal{#1}{07}}{Jul}{}%
\ifthenelse{\equal{#1}{08}}{Aug}{}%
\ifthenelse{\equal{#1}{09}}{Sep}{}%
\ifthenelse{\equal{#1}{10}}{Oct}{}%
\ifthenelse{\equal{#1}{11}}{Nov}{}%
\ifthenelse{\equal{#1}{12}}{Dec}{}}

% Style settings
\pagestyle{empty}
\setlength{\parindent}{0in}
\renewcommand{\thefootnote}{\fnsymbol{footnote}} % change footnote symbols

% Macros
\newenvironment{myresume}[2]{\pdfbookmark{#1}{#1}{\LARGE{#1}}\vspace{1mm}\hrule\vspace{-3mm}\begin{longtable}{p{0.12\textwidth} p{0.83\textwidth}}~&#2}{\end{longtable}}
    \renewcommand{\section}[2]{\vspace{-1.3em}\\\pdfbookmark{#1}{#2}{\singlespace\textsc{#1}}&}
\newcommand{\firstentry}[1]{\newline#1}
\newcommand{\entry}[1]{\vspace{-0.8em}\\~&#1}
\newcommand{\hide}[1]{}

% Datestamp format: \datestamp{YEAR}{MONTH}{DAY}
%\newcommand{\datestamp}[3]{\longmonth{#2} #3, #1}
%\newcommand{\datestamp}[3]{\shortmonth{#2} #3, #1}
\newcommand{\datestamp}[3]{\shortmonth{#2} #1}

%%%%%%%%%%%%%%%%
%% NAME BLOCK %%
%%%%%%%%%%%%%%%%

\begin{document}
\begin{myresume}{Sharmila Duppala}
    {\small
    email: \href{mailto:sduppala@umd.edu}{\textit{sduppala@umd.edu}}\hfill \href{https://trinity24.github.io/}{website:trinity24.github.io} \hfill Github: \href{https://github.com/trinity24}{@trinity24} \hfill Phone: +1 (202)-451-8473 }

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\section{Education}{education}

\firstentry{
    \href{http://www.umd.edu}{\textbf{University of Maryland}}, College Park, Maryland, USA \hfill \datestamp{2019}{08}{07}--Present\newline
    M.S. and Ph.D., \href{http://www.cs.umd.edu}{Department of Computer Science} \hfill 
}

\entry{
    \href{http://www.stonybrook.edu}{\textbf{Stony Brook University}}, New York, USA \hfill \datestamp{2017}{07}{20}--\datestamp{2019}{05}{15}\newline
    M.S. (Thesis track),  \href{http://cse.iitkgp.ac.in}{Department of Computer Science} \hfill
}

\entry{
    \href{http://www.svnit.ac.in}{\textbf{National Institute of Technology Surat}}, Gujarat, India \hfill \datestamp{2012}{07}{20}--\datestamp{2016}{05}{15}\newline
    B.Tech.,  \href{http://cse.iitkgp.ac.in}{Department of Computer Science and Engineering} \hfill 
}

%%%%%%%%%%%%%%%%%%
%% PUBLICATIONS %%
%%%%%%%%%%%%%%%%%%



    
%%%%%%%%%%%%%%%%%%%%%%%%%
%% RESEARCH EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research \newline Experience}{research}
\firstentry{
    \textbf{Ph.D. Student, \href{http://www.cs.umd.edu/}{University of Maryland, College Park}} \hfill \datestamp{2019}{08}{07}--Present \newline
    {\textit{ Algorithmic Fairness, and } \hfill \textbf{Prof. John P. Dickerson, Prof. Aravind Srinivasan} \newline \textit{ Stochastic Models for Combinatorial Optimization}} 
    }
    
    Worked on PAF (Probabilistically Approximately Fair) algorithms for combinatorial problems. Specifically designed and analyzed randomized algorithms to ensure fairness in various combinatorial problems like graph matching, set packing, set covering, and clustering problems with real-world applications. 

    
\entry{
    \textbf{Masters Thesis , Stony Brook University} \hfill \datestamp{2017}{07}{15}--\datestamp{2019}{05}{15} \newline
    {\textit{Memory and makespan tradeoff in parallel programs}} \hfill \textbf{Prof. Rezaul Chowdh
ury}

Worked on a resource allocation problem that arises in scheduling parallel programs. Specifically worked on designing bi-criteria algorithms for allocating memory to optimize work and makespan simultaneously. 
    }
    
\section{Internship \newline Experience}{research}

    % Worked on formulating notions of fairness, translating them into rigorous mathematical objects, and incorporating them in classical algorithmic problems. Specifically,  fairness in hypergraph matching, online matching, clustering and kidney exchange markets and the role of stochasticity in obtaining fairness, with emphasis on how the latter can ensure socially fair algorithmic solutions.}

\firstentry{
    \textbf{Applied Scientist Internship , Optum Labs} \hfill \datestamp{2023}{06}{03}--\datestamp{2023}{08}{15} \newline
    {\textit{ Deep representation learning for  partially annotated } \hfill \textbf{Dr. Carlos W. Morato} \newline \textit{multi-label clustering of medical dialogues.}} 
    
    Designed and implemented a neural model for learning cluster representations for multi-labeled dialogue data. Also developed a scoring metric to map multi-label dialogue to uni-labeled segments of dialogue. 
} 



\entry{
    \textbf{Summer Research Internship, New Jersey Institute of Technology} \hfill \datestamp{2023}{06}{03}--\datestamp{2023}{08}{15} \newline
    {\textit{Online matching under random order arrivals.}} \hfill \textbf{Prof. Pan Xu}  
} 

    Worked on online bipartite matching problem with bounded degree on the offline vertices, specifically we design algorithms with degree-dependent competitive ratio. 



%%%%%%%%%%%%%%%%%%%%%%%%%
%% INTERNSHIPS %%
%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%
%% KEY COURSES %%
%%%%%%%%%%%%%%%%%%



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% POSITIONS OF RESPONSIBILITY %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\href{https://scholar.google.com/citations?user=l7VcIesAAAAJ&hl=en}{Publications}}{papers}




\firstentry{{\textbf{{Robust Fair Clustering with Noisy Memberships}}}

\textit{Under submission at ICML 2024}}

\textit{Sharmila Duppala}, Seyed Esmaeili, Juan Luque, John Dickerson

\entry{{\textbf{{Proportionally Fair Matching}}}

\textit{Under submission at ICML 2024}}

\textit{$^{abc}$Sharmila Duppala}, Nathaniel Grammel, Juan Luque, Aravind Srinivasan

\entry{{\textbf{{Simultaneous Group and Individual Fairness in Set Covering Problems}}}

\textit{$^{abc}$Sharmila Duppala}, Nathaniel Grammel, Aravind Srinivasan

\textit{Under submission at ICML 2024}}

% \entry{{\textbf{{Concentration of Submodular Functions Under Negative Dependence}}}

% \textit{$^{abc}$Sharmila Duppala}, George Z. Li, Juan Luque, Aravind Srinivasan, Renata Valieva 

% \textit{Under submission at ITCS 2023}}


\entry{{\textbf{{Barter Exchange with Shared Item Valuations}}}

 Juan Luque, \textit{Sharmila Duppala}, John P. Dickerson, Aravind Srinivasan 

\textit{TheWebConference (WWW) 2024}}

% \entry{{\textbf{{Probabilistic Proportionally Fair Matching }}}

% \textit{Sharmila Duppala}, Nathaniel Grammel, Juan Luque, Aravind Srinivasan 

% \textit{In preparation}}




% \entry{{\textbf{{Robust Fair Clustering with Noisy Group Memberships}}}

%  \textit{Sharmila Duppala}, Seyed Esmaeili

% \textit{In preparation}}


% \entry{{\textbf{{Algorithms for online matching under random order with degree-dependent competitive ratios }}}

% \textit{Sharmila Duppala}, Pan Xu 

% \textit{In preparation}}


\entry{{\textbf{{Group Fairness in Set Packing Problems}}}

\textit{Sharmila Duppala}, Juan Luque, John P. Dickerson, Aravind Srinivasan 

\textit{IJCAI 2023}}

\entry{{\textbf{Rawlsian Fairness in Online Bipartite Matching:Two-sided, Group, and Individual}}

{Seyed Esmaeili, \textit{Sharmila Duppala}, Vedant Nanda, John P. Dickerson, Aravind Srinivasan}

\textit{AAAI 2023} }

    \entry{
       {\textbf{Online minimum matching with uniform metric and random arrivals }}
        
       $^{abc}$\textit{ Sharmila Duppala}, Karthik Sankararaman, Pan Xu
        
        \textit{Operations Research Letters 2022}
    }
    
\entry{{\textbf{{Fair labelled Clustering}}}

Seyed Esmaeili, \textit{Sharmila Duppala}, Brian Brubach, John P. Dickerson

\textit{KDD 2022} }


    \entry{
        \href{https://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=9359209}{\resizebox{\linewidth}{!}{\textbf{Improved MapReduce Load Balancing through Distribution-Dependent Hash Function Optimization}}}
        
        $^{abc}$ Zafar Ahmad, \textit{Sharmila Duppala}, Rezaul Chowdhury, Steven Skiena
        
        \textit{ICPADS 2020}
    }




    \entry{
        \href{https://dl.acm.org/doi/pdf/10.1145/3323165.3323209}{\textbf{Data Races and the Discrete Resource-time Tradeoff Problem with Resource Reuse over Paths}}
        
         {Rathish Das, Shih-Yu Tsai, \textit{Sharmila Duppala}, Jason Lynch, Ester Arkin, Rezaul Chowdhury, Joseph Mitchell, Steven Skiena}
         
        \textit{SPAA 2019}
    }



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% KEY COURSE PROJECTS %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Key \newline Projects}{projects}

% \firstentry{\textbf{Comparing the efficacy of different data-preprocessing techniques in fair classification, University of Maryland}}
%  \hfill {Prof. Soheil Feizi} 

% {Compared the performance of recent data preprocessing techniques in fair classification (eg. Clustering) like data (reweighing techniques (RW), learning fairness representations (LFR), optimized pre-processing(OP) ) under the fairness metric "statistical parity" using open source toolkit AI Fairness 360 on standard data sets available. }

\firstentry{\textbf{Operating Systems, Stony Brook University}}
 \hfill {Prof. Michael Ferdman} 
{Built a  pre-emptive, multi-tasking {Operating System} from scratch. Implemented demand-paging, copy-on-fork and auto-growing stack functionalities. Created a compatible standard library and bash-like shell to interact with the kernal (OS).}

\entry{\textbf{Computational Geometry, Stony Brook University}}
\hfill{Prof. Joseph Mitchell}{}

{ The alpha-fatness and chord-arc scores are different measures of the "niceness" of polygons. They may prove useful in developing quantitative measures by which electoral districts may be determined illegal. This project includes software for implementing these measures together with preliminary results on random polygons. }


\entry{}{\textbf{Energy Consumption Prediction, Stony Brook University}}
 \hfill {Prof. Zhenhua Liu} 
 
{Predicting an year's electricity consumption using the electricity consumption of previous year, time series data at 15min interval for 365 days. Implemented SARIMA, SVM and LSTM models using PyTorch and compared the results for 10 homes. Also enhanced the predictions using smart meter data for various appliances of the same homes.}


\section{Key \newline Courses}{courses}
\firstentry{
    \textbf{Graduate Level:} Quantum Computing, Modern Discrete Probability, Mechanism Design for Social AI, Algorithmic Lowerbounds, Advanced Algorithms, Computational Geometry, Discrete Mathematics, Computer Vision, Operating Systems, Network Security.
}\\[-8pt]

\entry{
    \resizebox{\linewidth}{!}{\textbf{Data Science/ML:} Deep Learning Theory, Advanced Numerical Optimization, Algorithms in Machine Learning}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% TECHNICAL SKILLS %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Positions of \newline Responsibility}{por}

\firstentry{
\textbf{Program Committee Member-Reviewer; Sub-reviewer} 

The WebConference 2024, ICLR 2023, SODA 2023, SODA 2019 
}

% \entry{
%     \textbf{Organizer, Algorithmic Fairness Reading Group} \hfill \datestamp{2023}{09}{01}-- \newline
%     Responsible for organizing Fairness bi-weekly seminar internally within University of Maryland. 
% }

\entry{
    \textbf{Organizer, Capital Area Theory Seminar and Algorithmic Fairness Seminar} \hfill \datestamp{2021}{08}{01}--Present \newline
    Responsible for co-organizing CS theory weekly seminar  hosting external speakers and a reading group discussing the latest papers in fairness literature. 
}

\entry{
    \textbf{Graduate Teaching Assistant} \hfill \datestamp{2017}{07}{14}--Present \newline
    Advanced Algorithms (Fall 2023), Analysis of Algorithms (Fall 2018), Computer Systems (Spring 2020) and Discrete Structures (Summer 2020)
}

\entry{
  \textbf{Curriculum Designer and Instructor, Girls Talk Math} \hfill \datestamp{2021}{06}{01}--\datestamp{2021}{08}{01} \newline
    Responsible for designing curriculum on undergraduate mathematics topics like Group Theory, Network Theory and Quantitative Finance for high school students and conducting educational camps.
}
\section{Technical Skills}{pls}
\firstentry{  
\textbf{Programming Languages:} C, C++, Java, Python, SQL, PL-SQL, MATLAB, Prolog, Qiskit 
}\\[-24pt]

\entry{ 
\textbf{Platforms/Tools:} Linux, Pandas, Windows, GDB, Eclipse, QEMU, Processing 
} 
\entry{   
\textbf{Libraries for Machine Learning:} PyTorch, Numpy, TensorFlow, Jupyter Notebook, Hugging Face.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACADEMIC HONORS & AWARDS %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Academic Awards}{aws}
\firstentry{
Chair's Fellowship, University of Maryland, College Park}\\[-24pt]
\entry{
TCS (Theoretical Computer Science) Women Scholarship STOC-2018  }
\entry{
ACM Travel Scholarship SPAA-2019 }
\entry{
TCS (Theoretical Computer Science) Women Scholarship STOC-2019 }


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% REFERENCES %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{References}{ref}
\firstentry{
Prof. Aravind Srinivasan, University of Maryland, College Park \hfill email: \href{mailto: srin@cs.umd.edu}{\textit{srin@cs.umd.edu}}
}
\entry{
Prof. John P. Dickerson, University of Maryland, College Park \hfill email: \href{mailto:johnd@umd.edu}{\textit{johnd@umd.edu}}
}
\entry{
Prof. Rezaul Chowdhury, Stony Brook University \hfill email: \href{mailto:rezaul@cs.stonybrook.edu}{\textit{rezaul@cs.stonybrook.edu}}
}
\end{myresume}
\end{document}
